Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-03 paper/paper.tex
pass

%\vspace{0.5ex}
\noindent\textbf{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks considered in our analysis.  Non-http attacks are listed at 
the top of the table and http attacks are listed at the bottom. Recall from
Section~\ref{sec:reverse-engineering} that (1) http attacks are
prevalent, (2) most http attacks use only content options, and (3)
most non-http attacks use field options only. We selected
\numNonContentAttacks\ non-http attacks and \numContentAttacks\ http
attacks. The higher number of http attacks reflects their
popularity. ``Name'' is the name of the attack,
``Source'' is the source where we obtained data to reproduce the
attack (see Section~\ref{subsec:malicious-traffic}), ``Type''
is the kind of attack, ``Protocol'' is the
protocol explored in the attack, and ``Ground Truth'' is the
rule options to capture the attack. The rationale for the selection
were (1) to cover various kinds of attacks and (2) to cover attacks of
various protocols. Considering (1), the selection includes attacks of
the following types: Denial-of-Service (DoS)~\cite{denial-of-service},
Active Reconnaissance (AREC)~\cite{active-reconnaissance}, Privilege
escalation (PESC)~\cite{privilege-escalation}, Remote Code Execution
(RCE)~\cite{remote-code-execution}, Local File Inclusion
(LFI)~\cite{local-file-inclusion} and ICMP Traffic Alerts \cite{icmp-types}.

@@

\noindent\textbf{Benign traffic.}~Public data sets of benign traffic
exist and can be used to evaluate the rate of false positives of
security tools. We used two popular public sources. The Bigflows.pcap
data set is part of the TcpReplay~\cite{tcpreplay} open source
project. It includes real network traffic of a private network. We
also used data sets from the Stratosphere IPS
Project~\cite{stratosphere-normal} including, for example, the regular
traffic of a university network.

@@

    \midrule
    Black Nurse & 1 & 4 & 9 & 2 \\    
    Ping Scan & 6 & 5 & 9 & 2 \\
    SYN Flood & 4 & 2 & 2 & 1 \\
    UDP Teardrop & 1 & 4 & 8 & 4 \\
    ICMP Info: Ping & 13 & 8 & 18 & 2 \\
    Dst/Host Unreachable & 132 & 6 & 3 & 1 \\
    Dst/Net Unreachable & 12 & 6 & 25 & 1 \\
    Dst/Port Unreachable & 3 & 6 & 12 & 1 \\
    ICMP Info: Echo Reply & 15 & 8 & 9 & 2 \\
    ICMP Info: Code 13 & 4 & 6 & 3 & 1 \\
    ICMP Info: Code 10 & 195 & 6 & 2 & 1 \\
    %%UDP Flood & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & 2 & 65 & - & - \\
    ColdFusion & 7 & 19 & 40 & 2\\
    iisadmin access & 3 & 17 & 605 & 1 \\        
    JBoss JMX & 5 & 23 & 925 & 36 \\
    scripttag & 23 & 22 & 2,221 & 1 \\
    WeBid LFI & 1 & 23 & 35,444 & 29\\    
    %%Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 852 & 1\\
    .idq access & 14 & 19 & 806 & 2 \\
    /system32/ in URI & 4 & 20 & 1,881 & 1 \\
    Basebuilder LFI & 1 & 22 & 60,222 & 55 \\
    Tomcat Snoop Access & 1 & 24 & 58,122 & 6 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[t!]
  \footnotesize
  \setlength{\tabcolsep}{8pt}
  %\setlength{\tabcolsep}{5pt}
  \renewcommand{\arraystretch}{-0.01}
  \caption{\label{table:weights}Contribution of heuristic functions.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrrrr}
    \toprule
    Name &
    base &
    -f1 &
    -f2 &    
    -f3 &
    -f4 \\
    \midrule
    Black Nurse & 2 & 7$\uparrow$ & 2 & 2 & 2 \\    
    Ping Scan & 2 &  8$\uparrow$& 2 & 2 & 2 \\
    SYN Flood & 1 & 1 & 1 & 1 & 1 \\
    ICMP Info: Ping & 2 & 18$\uparrow$& 2 & 2 & 2 \\
    Dst/Host Unreachable & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    Dst/Net Unreachable & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    Dst/Port Unreachable & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    ICMP Info: Echo Reply & 2 & 9$\uparrow$ & 2 & 2 & 2 \\
    ICMP Info: Code 13 & 1 & 2$\uparrow$ & 1 & 1 & 1 \\
    ICMP Info: Code 10 & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    %%UDP Flood & - & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & - & - & - & - & - & -\\
    ColdFusion & 2 & 2 & 2 & 7$\uparrow$ & 5$\uparrow$ \\
    iisadmin access & 1  & 1 & 1 & 1 & 14$\uparrow$\\        
    JBoss JMX & 36 & 36 & 14\cellcolor{lightgray}$\downarrow$ & 34\cellcolor{lightgray}$\downarrow$ & 269$\uparrow$ \\
    scripttag & 1 & 1 & 3$\uparrow$ & 1 & 15$\uparrow$ \\
    WeBid LFI & 29 & 29 & 72$\uparrow$ & 39$\uparrow$ & 41$\uparrow$ \\    
    %%Wordpress Login & 8 & - & - & - & - \\
    .htaccess access & 1  & 1 & 1 & 1 & 11$\uparrow$\\
    .idq access & 2  & 2 & 2 & 1\cellcolor{lightgray}$\downarrow$ & 15$\uparrow$ \\
    /system32/ in URI & 1  & 1 & 4$\uparrow$ & 1 & 15$\uparrow$\\
    Basebuilder LFI & 55  & 55 & 320$\uparrow$ & 112$\uparrow$ & 58$\uparrow$\\
      Tomcat Snoop Access & 6 & 6 & 3$\cellcolor{lightgray}\downarrow$ & 6 & 2,665$\uparrow$\\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

%\vspace{0.5ex}
\noindent\textbf{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks considered in our analysis.  Non-http attacks are listed at 
the top of the table and http attacks are listed at the bottom. Recall from
Section~\ref{sec:reverse-engineering} that (1) http attacks are
prevalent, (2) most http attacks use only content options, and (3)
most non-http attacks use field options only. % We selected
%\numNonContentAttacks\ non-http attacks and \numContentAttacks\ http
%attacks. The higher number of http attacks reflects their popularity.
``Name'' is the name of the attack,
``Source'' is the source where we obtained data to reproduce the
attack (see Section~\ref{subsec:malicious-traffic}), ``Type''
is the kind of attack, ``Protocol'' is the
protocol explored in the attack, and ``Ground Truth'' is the
rule options to capture the attack. The rationale for the selection
were (1) to cover various kinds of attacks and (2) to cover attacks of
various protocols. Considering (1), the selection includes attacks of
the following types: Denial-of-Service (DoS)~\cite{denial-of-service},
Active Reconnaissance (AREC)~\cite{active-reconnaissance}, Privilege
escalation (PESC)~\cite{privilege-escalation}, Remote Code Execution
(RCE)~\cite{remote-code-execution}, Local File Inclusion
(LFI)~\cite{local-file-inclusion} and ICMP Traffic Alerts \cite{icmp-types}.

@@

\noindent\textbf{Benign traffic.}~Public data sets of benign traffic
exist and can be used to evaluate the rate of false positives of
security tools. We used two popular public sources. The bigFlows.pcap
data set is part of the TcpReplay~\cite{tcpreplay} open source
project. It includes real network traffic of a private network. We
also used data sets from the Stratosphere IPS
Project~\cite{stratosphere-normal} including, for example, the regular
traffic of a university network.

@@

    \midrule
    Black Nurse & 1 & 4 & 9 & 2 \\    
    Ping Scan & 6 & 5 & 9 & 2 \\
    SYN Flood & 4 & 2 & 2 & 1 \\
    UDP Teardrop & 1 & 4 & 8 & 3 \\
    ICMP Info: Ping & 13 & 8 & 18 & 2 \\
    Dst/Host Unreachable & 132 & 6 & 3 & 1 \\
    Dst/Net Unreachable & 12 & 6 & 25 & 1 \\
    Dst/Port Unreachable & 3 & 6 & 12 & 1 \\
    ICMP Info: Echo Reply & 15 & 8 & 9 & 2 \\
    ICMP Info: Code 13 & 4 & 6 & 3 & 1 \\
    ICMP Info: Code 10 & 195 & 6 & 2 & 1 \\
    %%UDP Flood & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & 2 & 65 & - & - \\
    ColdFusion & 7 & 19 & 40 & 2\\
    iisadmin access & 3 & 17 & 605 & 1 \\        
    JBoss JMX & 5 & 23 & 925 & 36 \\
    scripttag & 23 & 22 & 2,221 & 1 \\
    WeBid LFI & 1 & 23 & 35,444 & 29\\    
    %%Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 852 & 1\\
    .idq access & 14 & 19 & 806 & 2 \\
    /system32/ in URI & 4 & 20 & 1,881 & 1 \\
    Basebuilder LFI & 1 & 22 & 60,222 & 55 \\
    Tomcat Snoop Access & 1 & 24 & 58,122 & 6 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[t!]
  \footnotesize
  \setlength{\tabcolsep}{8pt}
  %\setlength{\tabcolsep}{5pt}
  \renewcommand{\arraystretch}{-0.01}
  \caption{\label{table:weights}Contribution of heuristic functions.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrrrr}
    \toprule
    Name &
    base &
    -f1 &
    -f2 &    
    -f3 &
    -f4 \\
    \midrule
    Black Nurse & 2 & 7$\uparrow$ & 2 & 2 & 2 \\    
    Ping Scan & 2 &  8$\uparrow$& 2 & 2 & 2 \\
    SYN Flood & 1 & 1 & 1 & 1 & 1 \\
      UDP Teardrop & 3 & 5$\uparrow$ & 2 \cellcolor{lightgray}$\downarrow$ & 3 & 3 \\
    ICMP Info: Ping & 2 & 18$\uparrow$& 2 & 2 & 2 \\
    Dst/Host Unreachable & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    Dst/Net Unreachable & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    Dst/Port Unreachable & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    ICMP Info: Echo Reply & 2 & 9$\uparrow$ & 2 & 2 & 2 \\
    ICMP Info: Code 13 & 1 & 2$\uparrow$ & 1 & 1 & 1 \\
    ICMP Info: Code 10 & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    \midrule
    %%Apache Struts 2 & - & - & - & - & - & -\\
    ColdFusion & 2 & 2 & 2 & 7$\uparrow$ & 5$\uparrow$ \\
    iisadmin access & 1  & 1 & 1 & 1 & 14$\uparrow$\\        
    JBoss JMX & 36 & 36 & 14\cellcolor{lightgray}$\downarrow$ & 34\cellcolor{lightgray}$\downarrow$ & 269$\uparrow$ \\
    scripttag & 1 & 1 & 3$\uparrow$ & 1 & 15$\uparrow$ \\
    WeBid LFI & 29 & 29 & 72$\uparrow$ & 39$\uparrow$ & 41$\uparrow$ \\    
    %%Wordpress Login & 8 & - & - & - & - \\
    .htaccess access & 1  & 1 & 1 & 1 & 11$\uparrow$\\
    .idq access & 2  & 2 & 2 & 1\cellcolor{lightgray}$\downarrow$ & 15$\uparrow$ \\
    /system32/ in URI & 1  & 1 & 4$\uparrow$ & 1 & 15$\uparrow$\\
    Basebuilder LFI & 55  & 55 & 320$\uparrow$ & 112$\uparrow$ & 58$\uparrow$\\
      Tomcat Snoop Access & 6 & 6 & 3$\cellcolor{lightgray}\downarrow$ & 6 & 2,665$\uparrow$\\
    \bottomrule
  \end{tabular}
\end{table}
